site_map

### 2020-07-23 site_map.Rmd
update

# Determining the temperature at the various distances from the coast
```

@@

# write.csv(site_list_sub,file = "site_list_sub.csv")
# Define plotting parameters
sa_lats <- c(-37, -27); sa_lons <- c(14, 25)

>>>>

## Determining the temperature at the various distances from the coast
```

@@

# Define plotting parameters
sa_lats <- c(-37, -27); sa_lons <- c(14, 25)
